Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-10-17 sports_analytics.Rmd
Elo chess k-factor

Another widely known tool for measuring team strength is the Elo rating system [@Elo1978], which was originally developed for chess.
Given two players $i$ and $j$ with unknown ratings $R_i$ and $R_j$, the probability $\Pi_{ij}$ of $i$ beating $j$ is defined as
$$
\Pi_{ij} = \frac{1}{1 + K^{(R_j - R_i)/400}} \,.
$$
In this formula, $K$ is commonly known as the $K$-factor (or development coefficient).
The International Chess Federation (FIDE) chooses $K=10$ for the calculation of Elo ratings.

@@

[Mention glicko as an alternative to improve Elo]

>>>>

Another widely known tool for measuring team strength is the Elo rating system [@Elo1978], which was originally developed for chess.
Given two players $i$ and $j$ with unknown ratings $R_i$ and $R_j$, the probability $\Pi_{ij}$ of $i$ beating $j$ is defined as
$$
\Pi_{ij} = \frac{1}{1 + K^{(R_j - R_i)/400}} \,.
$$
In this formula, $K$ is commonly known as the $K$-factor, or development coefficient.
The International Chess Federation (FIDE) uses $K=10$ for players with any previously achieved rating of at least 2400.
For those that have never reached a rating of 2400 or better, $K=20$ is assigned. 
Finally, $K=40$ is given to new players with under 30 games played, and players under the age of 18 with rating fewer than 2300 [@fide2022rating].

@@
